% Abstract: each about 1/2 page
% http://williamstallings.com/Extras/Abstract.html
% Motivation (Why do we care?)
% Problem statement (What problem are we trying to solve?)
% Approach (How did we go about it)
% Results (What’s the answer?)
% Conclusion (What are the implications of the answer?)

\begin{abstract}
Following the birth of cryptocurrencies back in 2008, internet investment platforms called exchanges were created to integrate these cryptocurrencies. Allowing investors to sell and buy assets fairly and agile. Exchanges now have become popular and carry out over $99\%$ of all daily transactions, totaling hundreds of millions of dollars. Despite that exchanges handling large quantities of money, the industry remains mostly unregulated.

As these exchanges remain unregulated, they are and will continue to be susceptible to price manipulation schemes as they are legal to perform by law. Over the years, exchanges have become an attractive ground where scammers execute various price manipulation schemes that aim to leech assets from ordinary investors. One particular scheme have risen in popularity over the years, and are often witnessed on exchanges, and that one is termed \ac{pd}. This scheme has a history from all the way back in 1700 and is still active and troublesome for investors today.

In this thesis, we present \project, a system that seeks to detect \acsp{pd} in real-time using deep learning. Throughout this thesis, we retrieved, prepared, labeled, processed a dataset to train a model that identifies \acsp{pd}. With a high accuracy the model surpasses previously proposed model accuracy-wise in the detection of this fraudulent scheme.
\end{abstract}